---
title: "AnalysisLin-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AnalysisLin-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
- [**Introduction**](#introduction)
- [**Descriptive Statistic**](#descriptive-statistic)
- [**Data Visualization**](#data-visualization)
  - [Numeric Plot](#numeric-plot) 
  - [Categorical Plot](#categorical-plot) 
- [**Correlation Analysis**](#correlation-analysis)
  - [Correlation Matrix](#correlation-matrix) 
  - [Correlation Clustering](#correlation-clustering) 
- [**Feature Engineering**](#feature-engineering)
  - [Missing Value Imputation](#missing-value-imputation) 
  - [Principle Component Analysis](#principle-component-analysis)
  
# Introduction
Hi everyone, this page is to introduce the package AnalysisLin, which is my personal package for exploratory data analysis. You can find the source package on my Github: [https://github.com/Zhiwei2799/AnalysisLin](https://github.com/Zhiwei2799/AnalysisLin)

There are several useful functions in this package, and table below summarize the functions that would be going over in this page
```{r,echo=FALSE}
library(knitr)
```

```{r}
df <- data.frame(
  Descriptive_Statistics = c("desc_stat()",""),
  Data_Visualization = c("numeric_plot()", "categoric_plot()"),
  Correlation_Analysis = c("corr_matrix()", "corr_cluster()"),
  Feature_Engineering = c("missing_impute()", "automate_pca()")
)
kable(df)
```
Famous and very useful pre-installed datasets, such as iris, mtcars, and airquality, would be used for this document to demonstrate what does each function in the package do. If you have not installed the package, please do the following:
```{r}
install.packages("/Users/zhiweilin/Desktop/My package/AnalysisLin_0.1.0.tar.gz", repos = NULL, type = "source")
library(AnalysisLin)
```

```{r}
data("iris")
data("mtcars")
data("airquality")
```


Exploratory Data Analysis, in simple words, is the process to get to know your data. 

## Descriptive Statistic
First function in package is desc_stat. This function computes numerous useful statistical metrics so that you gain a profound understanding of your data

- **Count**: Number of values in a variable.
- **Unique**: Number of values that are unique in a variable.
- **Duplicate**: Number of rows that are duplicate in a dataset.
- **Null**: Number of values that are missing in a variable.
- **Null Rate**: Percentage of values that are missing in a variable.
- **Type**: Type of variable (e.g., numeric, character, factor).
- **Min**: Smallest value.
- **P25**: Median of the first half.
- **Mean**: Mean value.
- **Median**: Median value.
- **P75**: Median of the second half.
- **Max**: Largest value.
- **SD**: Standard deviation.
- **Kurtosis**: A measure of the tailedness of a distribution.
- **Skewness**: A measure of the asymmetry of a distribution.
- **Jarque-Bera Test P-value**: P-value from the Jarque-Bera test that checks whether data have the skewness and kurtosis matching a normal distribution.
```{r}
desc_stat(iris)
```

```{r}
desc_stat(mtcars)
```

```{r}
desc_stat(airquality)
```

These metrics provide valuable insights into the dataset in a deep level. If you don't want any of these metrics to be computed, you can set them to `FALSE`. This way, the unwanted metrics won't appear in the output.

For example, if you don't want kurtosis,skewness and jarque_pvalue for mtcar dataset:
```{r}
desc_stat(mtcars,kurtosis = F,skewness = F,jarque_test = F)
```
## Data Visualization
### Numeric Plot 
To visualize histogram for all numerical variables
```{r}
numeric_plot(iris)
```
if you want to add distribution curve over histogram:
```{r}
numeric_plot(iris,prob=T,dens=T)
```
### Categorical Plot 
To visualize bar/pie charts for all categorical variables
```{r}
categoric_plot(iris,bar_width = 1)
```

if you just want bar or pie chart:
```{r,results = 'hide'}
categoric_plot(iris,bar=F)
```

```{r,results = 'hide'}
categoric_plot(iris,pie=F)
```

## Correlation Analysis
### Correlation Matrix
To visualize correlation table for all variables.
```{r}
corr_matrix(mtcars)
```
if you want to visualize correlation map along with correlation table:
```{r}
corr_matrix(mtcars,corrplot=T)
```
you may also choose type of correlation:Pearson correlation and Spearman correlation.
```{r,results = 'hide'}
corr_matrix(mtcars,type='pearson')
corr_matrix(mtcars,type='spearman')
```

### Correlation Clustering
Correlation clustering partitioning data points into groups based on their similarity(correlation)
```{r}
corr_cluster(mtcars,type='pearson')
```

```{r}
corr_cluster(mtcars, type='spearman')
```


## Feature_Engineering
### Missing Value Imputation
Imputing mssing value is a way to get more information from a data with missing values. However, one need to carefully choose what method to use to impute missing values in order to reach most accuracy.

- **mean**: use mean value to replace missing value.  

```{r}
impute_missing(airquality,method='mean')
```

- **mode**: use most frequency value to replace missing value.  

- **median**: use median value to replace missing value.  

- **locf**: use last observation value to replace missing value.  

- **knn**: use k-nearest nerighbor to replace missing value, k needs to be chosen.   
```{r,results = 'hide',message=FALSE}
impute_missing(airquality,method='mode')
impute_missing(airquality,method='median')
impute_missing(airquality,method='locf')
impute_missing(airquality,method='knn',k=5)
```

### Principle Component Analysis
Principle Component Analysis can help you to reduce the number of variables in a dataset.
To perform and visualize PCA on some selected variables

```{r}
automate_pca(mtcars,variance_threshold = 0.9)
```

